pdp: An R Package for Creating Partial Dependence Plots

### 2016-09-13 manuscript/greenwell.tex
edited summary
more tweaks to summary

In this paper, we showed how to construct PDPs for various types of black box models in R using the \pkg{pdp} package. We also briefly discussed related approaches availble in other R packages as well. Suggestions to avoid extrpolation and high excecution times were discussed and demonstrated via examples. In terms of future development, \pkg{pdp} can be expanded in a number of ways. For example, it would be useful to have the ability to construct PDPs for black box survival models---like conditional random forests with censored response.

>>>>

PDPs can be used to graphically examine the dependence of the response on low cardinality subsets of the features, accounting for the average effect of the other predictors. In this paper, we showed how to construct PDPs for various types of black box models in R using the \pkg{pdp} package. We also briefly discussed related approaches availble in other R packages as well. Suggestions to avoid extrpolation and high excecution times were discussed and demonstrated via examples. In terms of future development, \pkg{pdp} can be expanded in a number of ways. For example, it would be useful to have the ability to construct PDPs for black box survival models---like conditional random forests with censored response. It would also be nice to implement the partial dependence-based $H$-statistic \citep{friedman-2008-predictive} for assessing the strength of interaction between predictors.
